\Large {\bf Protocol-Guided Analysis of Post-silicon Traces Under Limited Observability}

### 2015-09-11 paper.tex
Done editing intro

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\Large {\bf Flow-Guided Analysis of System-level Post-silicon
  Traces Under Limited Observability}}

@@

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\Large {\bf Protocol-Guided Analysis of Post-silicon
  Traces Under Limited Observability}}

@@

An SoC design is typically composed of a large number of
pre-designed hardware or software blocks (often referred to
as ``intellectual properties'' or ``IPs'') that coordinate
through complex protocols to implement system-level
behavior.  Fig.~\ref{fig:flow-spec-ex} shows one such
protocol, involving th
\begin{figure}[tb]
\begin{center}
\includegraphics[height=2.5in]{figures/bpmn-flow-ex}
\caption{A graphical representation of a SoC firmware load protocol in BPMN~\cite{Krstic14HOST}.}
\label{flow-spec-ex}
\end{center}
\end{figure}
